AP/PA Tables ITHIM Global

### 2022-01-19 summary_tables_PA_AP.Rmd
Create excel sheet. Ref #86

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyr)
library(dplyr)
#library(plotly)
#library(htmltools)

@@

>>>>

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyverse)
#library(plotly)
#library(htmltools)

@@

output_file <- "results/multi_city/AP/desc_stats.xlsx"
writexl::write_xlsx(list(PM_2.5_emission_inventory = sl,
                         CO2_emissions = cl,
                         summary_stats_PM2.5_CO2 = bind_rows(l)), path = output_file)
